Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-06-28 sm.tex
SM references, use and show shorten url

\section{Simulation of Raman sideband cooling}

@@

We use a computer simulation to study the importance of different effects
and guide the optimization of cooling. The simulation uses quantum jump method to accurately
calculate the evolution within each laser pulse while different energy eigenstates are assumed
to decohere immediately on spontaneous emission of photon and on pulse boundaries.
Such approxiations are valid for simulation of the cooling and greatly simplifies the computation
at the cost of limiting the applicability of the simulation to processes that requires stronger
coherence such as Ramsey spectroscopy and rapid push-out.

@@

Each pulse in general has a coherent part from the Raman drive (zero for optical pumping pulse)
and an incoherent part from scattering (optical pumping or off-resonance scattering).
This nicely fits the general formula of the quantum jump method. Due to the large number of
states that we need to take into account ($30-150$ states in each of the three axis and
$8$ hyperfine states, giving a total of $10^6$ states),
the generic wavefunction propagation is very inefficient.
Therefore, this is further simplified by reducing the number of states to be kept track of during
the coherent propagation and apply quantum jump using a set of reduced jump operator that
describes the total jump probability from a certain states (sum over all final states).
The coherent propagation is then accurately solved in order to avoid having to use a time step
much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://github.com/nacs-lab/yyc-data/blob/3b50baae233ba54456cc35260d91208a23021410/notes/precise-quantum-jump.pdf}{note about modification to the quantum jump method}}.

@@

The simulation is written in Julia. All code are available under GPLv3 license at
\footnote{\href{https://github.com/nacs-lab/yyc-data/tree/3b50baae233ba54456cc35260d91208a23021410/lib}{Library code}} and
\footnote{\href{https://github.com/nacs-lab/yyc-data/blob/3b50baae233ba54456cc35260d91208a23021410/calculations/sideband/sideband.jl}{Top level code}}

\end{document}

>>>>

\section{Simulation of 3D Raman sideband cooling}

@@

We use a computer simulation to study the importance of different effects
and guide the optimization of cooling.
The simulation uses quantum jump method\cite{Chretien2014} (or Monte-Carlo wavefunction method)
to accurately calculate the evolution within each laser pulse while different energy eigenstates
are assumed to decohere immediately on spontaneous emission of photon and on pulse boundaries.
Such approxiations are valid for simulation of the cooling and greatly simplifies the computation
at the cost of limiting the applicability of the simulation to processes that requires stronger
coherence such as Ramsey spectroscopy and rapid push-out.

@@

Each pulse in general has a coherent part from the Raman drive (zero for optical pumping pulse)
and an incoherent part from scattering (optical pumping or off-resonance scattering).
This nicely fits the general formula of the quantum jump method. Due to the large number of
states that we need to take into account ($30-150$ states in each of the three axis and
$8$ hyperfine states, giving a total of $10^6$ states),
the generic wavefunction propagation is very inefficient.
Therefore, this is further simplified by reducing the number of states to be kept track of during
the coherent propagation and apply quantum jump using a set of reduced jump operator that
describes the total jump probability from a certain states (sum over all final states).
The coherent propagation is then accurately solved in order to avoid having to use a time step
much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.

@@

The simulation is written in Julia. All code are available under GPLv3 license at
\footnote{\href{https://goo.gl/WLJwJp}{Library code (https://goo.gl/WLJwJp)}} and
\footnote{\href{https://goo.gl/XXVreq}{Top level code (https://goo.gl/XXVreq)}}

\bibliography{paper}
\end{document}
